Missing data: Current practice in football research and recommendations for

### 2020-09-11 paper/paper.Rmd
edit discussion text.
edit simulation code.

---
title: "Missing data: Current practice in football research and recommendations for improvement"
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
output: 
  html_document:
    toc: true
    toc_float: true
    keep_md: true
bibliography: references.bib
---

@@

Data does not go missing the same way every time. There are three broad
categorisations describing why data can be missing: Missing Completely
at Random (MCAR), Missing at Random (MAR), and Missing Not at Random
(MNAR). These categorisations help describe whether the missingness
occurs by chance (MCAR), due to some observed variable (MAR) or an
unobserved variable (MNAR), with MCAR being the least harmful, and MAR and MNAR
biased [@Newman2014]. Football relevant examples are provided in Supplement 1, and
more detailed explanations of MCAR, MAR, MNAR can be found elsewhere
[@Sainani2015; @Nakagawa2008; Sterne2009].

@@

## Missing data across the analysis pathway

@@

# Generate the x-variables
d <- get_afltables_stats(start_date = "2020-01-01", end_date = "2020-09-04")

data <-
  d %>% select(
    ID,
    Round,
    First.name,
    Surname
    )

@@

# Simulate number of sprints per game
Observations = nrow(data)
sprints <- sample.int(100, # numbers of sprints between 1 and 100
           nrow(data),
           replace = T) # observations

# Simulate incidence of hamstring strain injuries
# sample.int(100, # numbers of sprints between 1 and 100
#            nrow(data),
#            replace = T) # observations

data <- merge(data, sprints)

# Impute missing values
data <- ampute(data = df[,10:43])
data <- df_first_try$amp

# Put the dataset together
# Impute missing values
data <- ampute(data = df[,10:43])
data <- data$amp

>>>>

---
title: 'Missing data: Current practice in football research and recommendations for
  improvement'
bibliography: references.bib
output:
  word_document:
    toc: yes
  pdf_document:
    toc: yes
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
---

@@

Data does not go missing the same way every time. There are three broad
categorisations describing why data can be missing: Missing Completely
at Random (MCAR), Missing at Random (MAR), and Missing Not at Random
(MNAR). These categorisations help describe whether the missingness
occurs by chance (MCAR), due to some observed variable (MAR) or an
unobserved variable (MNAR), with MCAR being the least harmful, and MAR and MNAR
biased [@Newman2014]. Football relevant examples are provided in Supplement 1, and
more detailed explanations of MCAR, MAR, MNAR can be found elsewhere
[@Sainani2015; @Nakagawa2008; @Sterne2009].

@@

## Practices to avoid across the analysis pathway

@@

# Generate the x-variables
# d <- get_afltables_stats(start_date = "2020-01-01", end_date = "2020-09-04")
# 
# data <-
#   d %>% select(
#     ID,
#     Round,
#     First.name,
#     Surname
#     )

@@

# # Simulate number of sprints per game
# Observations = nrow(data)
# sprints <- sample.int(100, # numbers of sprints between 1 and 100
#            nrow(data),
#            replace = T) # observations
# 
# # Simulate incidence of hamstring strain injuries
# # sample.int(100, # numbers of sprints between 1 and 100
# #            nrow(data),
# #            replace = T) # observations
# 
# data <- merge(data, sprints)
# 
# # Impute missing values
# data <- ampute(data = df[,10:43])
# data <- df_first_try$amp
# 
# 
# 
# # Put the dataset together
# # Impute missing values
# data <- ampute(data = df[,10:43])
# data <- data$amp
